Tables and Figures - Supplement A and B

### 2019-12-03 code/04_tables.rmd
updated script names for clarity + minor updates to correlations code

source("helper_functions_tables_figures.r") #Load functions to prep data for figures
```

@@

## Table 3
### Heterogeneity across primary effects and statistical power of thirteen multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
```{r prep-heterogeneity-table, cache = TRUE}
#library(metafor)
#library(dplyr)
#library(purrr)

@@

>>>>

source("03_helper_functions_tables_figures.r") #Load functions to prep data for figures
```

@@

## Table 3
### Heterogeneity across primary effects and statistical power of thirteen multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
```{r prep-heterogeneity-table, cache = TRUE, results = 'hide'}
#library(metafor)
#library(dplyr)
#library(purrr)

@@

#****************
#Results for "Heterogeneity Estimates and Confidence Intervals" section in paper

sum(het$s_I2 >= 62.5) #what number of I2 estimates would be rounded to "large" (75% I2) heterogeneity
sum(het$s_I2 >= 37.5 & het$s_I2 < 62.5) #what number of I2 estimates would be rounded to "medium" (50% I2) heterogeneity
sum(het$s_I2 >= 12.5 & het$s_I2 < 37.5) #what number of I2 estimates would be rounded to "small" (25% I2) heterogeneity
sum(het$s_I2 < 12.5) #what number of I2 estimates would be rounded to zero (0% I2) heterogeneity

quantile(het$tau[het$effect_type == "r"]) #quantiles of tau for correlation tau scale
quantile(het$tau[het$effect_type == "SMD"]) ##quantiles of tau for SMD tau scale

sum(het$s_ci.lb == 0) #number of meta-analysis with lower I2 CI containing zero
sum(het$s_ci.lb == 0 & het$tau_ci.lb == 0) #All above also have lower tau CI containing zero

sum(het$s_I2 == 0) #number of meta-analyses with I2 estimates of zero
sum(het$s_I2 == 0 & het$tau == 0) #all these also have tau estimates of zero

#****************

#continue prepping table 3

### 2019-12-03 code/05_figures-and-correlations.rmd
updated script names for clarity + minor updates to correlations code

#1. Standardized mean differences----
SMDs <- tau2_per_type %>% filter(effect_type == "Standardized Mean Difference")

cor.test(SMDs$tau2, SMDs$eff_size) #pearson tau2
cor.test(SMDs$s_I2, SMDs$eff_size) #pearson I2
cor.test(SMDs$H2, SMDs$eff_size) #pearson H2

cor.test(SMDs$tau2, SMDs$eff_size, method = "spearman") #spearman
cor.test(SMDs$s_I2, SMDs$eff_size, method = "spearman") #spearman
cor.test(SMDs$H2, SMDs$eff_size, method = "spearman") #spearman

@@

cor.test(dropped_anchoring$s_I2, dropped_anchoring$eff_size) #pearson

@@

bootfit <- boot(data=SMDs, statistic=pear, R=1000, formula= ~ eff_size + s_I2)
I2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)

#Excluding anchoring effects
bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ eff_size + s_I2)

@@

#1.2 Tau2 confidence intervals----
pear <- function(formula, data, indices){
     d <- data[indices,]
     fit <- cor.test(formula = ~ tau2 + eff_size, data=d)
     return(fit$estimate)
}

bootfit <- boot(data=tau2_per_type, statistic=pear, R=1000, formula= ~ eff_size + tau2)

tau2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))

@@

bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ eff_size + tau2)

tau2_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)

@@

bootfit <- boot(data=tau2_per_type, statistic=pear, R=1000, formula= ~ eff_size + H2)

H2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))

@@

options(warn=-1)
bootfit <- boot(data=tau2_per_type, statistic=spear, R=1000, formula= ~ eff_size + s_I2)
options(warn=0)

@@

#Second for tau2
spear <- function(formula, data, indices){ #spearman
     d <- data[indices,]
     fit <- cor.test(formula = ~ tau2 + eff_size, data=d, method = "spearman")
     return(fit$estimate)
}

options(warn=-1)
bootfit <- boot(data=tau2_per_type, statistic=spear, R=1000, formula= ~ eff_size + tau2)
options(warn=0)

tau2_ci_spear <- boot.ci(bootfit, type=c("perc", "bca"))

#2. Fisher's z----
fish <- tau2_per_type %>% filter(effect_type == "Fisher's z" )
cor.test(fish$tau2, fish$eff_size) #pearson tau2
cor.test(fish$s_I2, fish$eff_size) #pearson I2
cor.test(fish$H2, fish$eff_size)

>>>>

#1. Standardized mean differences----
SMDs <- tau2_per_type %>% filter(effect_type == "Standardized Mean Difference") %>% 
  mutate(tau = sqrt(tau2))

cor.test(SMDs$tau, SMDs$eff_size) #pearson tau2
cor.test(SMDs$s_I2, SMDs$eff_size) #pearson I2
cor.test(SMDs$H2, SMDs$eff_size) #pearson H2

cor.test(SMDs$tau, SMDs$eff_size, method = "spearman") #spearman
cor.test(SMDs$s_I2, SMDs$eff_size, method = "spearman") #spearman
cor.test(SMDs$H2, SMDs$eff_size, method = "spearman") #spearman

@@

cor.test(dropped_anchoring$tau, dropped_anchoring$eff_size) #pearson
cor.test(dropped_anchoring$s_I2, dropped_anchoring$eff_size) #pearson
cor.test(dropped_anchoring$H2, dropped_anchoring$eff_size) #pearson

@@

#bootfit <- boot(data=SMDs, statistic=pear, R=1000, formula= ~ eff_size + s_I2) #see Fig 3
#I2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)

#Excluding anchoring effects
set.seed(234)
bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ eff_size + s_I2)

@@

#1.2 Tau2 confidence intervals----
pear <- function(formula, data, indices){
     d <- data[indices,]
     fit <- cor.test(formula = ~ tau + eff_size, data=d)
     return(fit$estimate)
}

# bootfit <- boot(data=tau2_per_type, statistic=pear, R=1000, formula= ~ eff_size + tau2) #see Fig 3
# tau2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))

@@

set.seed(423)
bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ eff_size + tau)
tau_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)

@@

set.seed(342)
bootfit <- boot(data=tau2_per_type, statistic=pear, R=1000, formula= ~ eff_size + H2)
H2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))

@@

set.seed(241)
options(warn=-1)
bootfit <- boot(data=tau2_per_type, statistic=spear, R=1000, formula= ~ eff_size + s_I2)
options(warn=0)

@@

#Second for tau
spear <- function(formula, data, indices){ #spearman
     d <- data[indices,]
     fit <- cor.test(formula = ~ tau + eff_size, data=d, method = "spearman")
     return(fit$estimate)
}

set.seed(5233)
tau2_per_type <- tau2_per_type %>% mutate(tau = sqrt(tau2))
options(warn=-1)
bootfit <- boot(data=tau2_per_type, statistic=spear, R=1000, formula= ~ eff_size + tau)
options(warn=0)

tau_ci_spear <- boot.ci(bootfit, type=c("perc", "bca"))

### 2019-12-03 code/06_Supplement-tables-figures.Rmd
updated script names for clarity + minor updates to correlations code

---
title: "Tables and Figures - Supplement A and B"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

@@

source("helper_functions_tables_figures.r") #Load functions to prep data for figures
```

##Supplement A

@@

```{r trunc-biserial, cache = TRUE}
#Transform effect sizes to biserial correlations (pearson's correlations left as is)
#estimate tau2 for correlations
#'transform_MA' and 'summarizer' are sourced functions
res2 <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map(transform_MA) %>% #
  map_dfr(summarizer, .id = "effect")

@@

d <- het %>% filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales') & effect_type == "SMD.") %>% 
  mutate(sigma2 = tau2/(I2/100) - tau2) #add 'typical within study variance' per project

@@

```{r c-plot-1, cache = FALSE}
c_plot_1 <- ggplot(d, aes(x = I2, y = sqrt(tau2))) + geom_point() + ggtitle("Biserial r (transformed SMD)")

@@

```{r untruncated-biserial, cache = TRUE}
res3 <- dat %>%
  filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales') & outcomes1_2 == "mean _ SD") %>% 
  split(.$effect) %>% 
  map(~transform_SD(.$outcome_t1, .$outcome_c1, .$outcome_t2, .$outcome_c2, .$ntreatment, .$ncontrol)) %>% 
  map(~untruncated_d_to_r(.$d, .$n1, .$n2)) %>% 
  map_dfr(summarizer, .id = "effect")
```

```{r c-plot, cache = FALSE}
c_plot <- c_plot_1 + geom_point(data = res3, shape = 4, aes(x = I2, y = sqrt(tau2))) +
  scale_x_continuous(name = expression(paste(italic(I)^2, " Index (biserial)"))) +
  scale_y_continuous(name = "Tau (biserial)")

@@

```{r tau-vs-tau}
b <- select(a, effect, tau2) %>% 
  left_join(select(d, effect, tau2), by = "effect") %>% #add truncated transformation tau2
  left_join(select(res3, effect, tau2), by = "effect") #add untruncated transformation tau2
```

```{r b-plot-1}
b_plot_1 <- ggplot(b, aes(x = sqrt(tau2.x), y = sqrt(tau2.y))) + 
  geom_point()

```{r b-plot}
b_plot <- b_plot_1 + geom_point(data = b, shape = 4, aes(x = sqrt(tau2.x), y = sqrt(tau2))) +
  ggtitle("SMD vs. biserial") +
  scale_x_continuous(name = "Tau (SMD)") +
  scale_y_continuous(name = "Tau (biserial)")
```

@@

##Supplement B

```{r Supplement-B-table}

@@

Estimated type I error and power for zero/small/medium/large heterogeneity when simulated with a true effect size of zero vs. medium are shown for each effect in Table A1. In both cases type I error is approximately nominal, as compared to the expected 5% error rate. With a true effect size of zero, average power was `r 100*round(mean(zero$Small), digits = 2)`%/`r 100*round(mean(zero$Medium), digits = 2)`%/`r 100*round(mean(zero$Large), digits = 2)`% for small/medium/large heterogeneity, respectively. The corresponding power with a true medium effect size was also `r 100*round(mean(zero$Small), digits = 2)`%/ `r 100*round(mean(zero$Medium), digits = 2)`%/`r 100*round(mean(zero$Large), digits = 2)`%, respectively. To conclude, changing true effect size in our simulations from zero to medium had little to no impact on estimated type I error and power.

>>>>

---
title: "Tables and Figures - Supplement A and B"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

@@

source("03_helper_functions_tables_figures.r") #Load functions to prep data for figures
```

## Supplement A

@@

```{r trunc-biserial, cache = TRUE}
#Transform effect sizes to biserial correlations (pearson's correlations left as is)
#estimate tau2 for correlations
#'transform_MA' and 'summarizer' are sourced functions
res2 <- dat %>%
  filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales')) %>%
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map(transform_MA) %>% #
  map_dfr(summarizer, .id = "effect")

@@

d <- het %>% filter(effect_type == "SMD.") %>%
  mutate(sigma2 = tau2/(I2/100) - tau2) #add 'typical within study variance' per project

@@

```{r c-plot-1, cache = FALSE}
c_plot <- ggplot(d, aes(x = I2, y = sqrt(tau2))) + geom_point() + ggtitle("Point Biserial r (transformed SMD)")

@@

```{r tau-vs-tau}
b <- select(a, effect, tau2) %>%
  left_join(select(d, effect, tau2), by = "effect") #add truncated transformation tau2
```

```{r b-plot-1}
b_plot <- ggplot(b, aes(x = sqrt(tau2.x), y = sqrt(tau2.y))) +
  geom_point() +
  ggtitle("SMD vs. Point biserial") +
  scale_x_continuous(name = "Tau (SMD)") +
  scale_y_continuous(name = "Tau (Point biserial)")

@@

@@

## Supplement B

```{r Supplement-B-table}
#Load simulation results (power/type 1 error for all effects)
dens <- readRDS("../data/power_simulation_results.RDS")
names(dens) <-  sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort

@@

Estimated type I error and power for zero/small/medium/large heterogeneity when simulated with a true effect size of zero vs. medium are shown for each effect in Table SB1. In both cases type I error is approximately nominal, as compared to the expected 5% error rate. With a true effect size of zero, average power was `r 100*round(mean(zero$Small), digits = 2)`%/`r 100*round(mean(zero$Medium), digits = 2)`%/`r 100*round(mean(zero$Large), digits = 2)`% for small/medium/large heterogeneity, respectively. The corresponding power with a true medium effect size was also `r 100*round(mean(zero$Small), digits = 2)`%/ `r 100*round(mean(zero$Medium), digits = 2)`%/`r 100*round(mean(zero$Large), digits = 2)`%, respectively. To conclude, changing true effect size in our simulations from zero to medium had little to no impact on estimated type I error and power.
